---
title: "Untitled"
author: "Suryadyuti Baral"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
begin = Sys.time()
library(dplyr)
library(refund)
library(tidyverse)
library(fdapace)

bootstrap_fpca_ci <- function(Y, nb_boot = 100, n_eig = 2, argvals = t, prob = c(.025, .975)) {
  # Y: subjects x time matrix (rows = subjects, columns = time points)
  # nb_boot: number of bootstrap samples
  # n_eig: number of eigenfunctions to extract (usually 1)
  
  n_subj <- nrow(Y)
  n_time <- ncol(Y)
  
  Ly <- lapply(seq_len(nrow(Y)), function(i) Y[i,])
  Lt <- lapply(seq_len(nrow(Y)), function(i) argvals)
  
  # Fit FPCA on original data
  fpca_fit <- FPCA(Ly, Lt)
  phi_hat <- fpca_fit$phi[, 1:n_eig, drop = FALSE]
  scores_hat <- fpca_fit$xiEst[, 1:n_eig, drop = FALSE]
  t_grid <- fpca_fit$workGrid
  
  # Store bootstrap results
  phi_boot <- array(NA, dim = c(length(t_grid), n_eig, nb_boot))
  scores_boot <- array(NA, dim = c(n_subj, n_eig, nb_boot))
  
  for (b in 1:nb_boot) {
    # Bootstrap subjects
    boot_ids <- sample(1:n_subj, n_subj, replace = TRUE)
    Y_boot <- Y[boot_ids, ]
    Ly <- lapply(seq_len(nrow(Y_boot)), function(i) Y_boot[i,])
    
    # Fit FPCA
    fpca_b <- try(FPCA(Ly, Lt), silent = TRUE)
    if (inherits(fpca_b, "try-error")) next
    
    # Align eigenfunction sign (since eigenfunctions are defined up to ±1)
    phi_b <- fpca_b$phi[, 1:n_eig, drop = FALSE]
    for (k in 1:n_eig) {
      sign_correction <- sign(sum(phi_b[, k] * phi_hat[, k]))
      phi_b[, k] <- sign_correction * phi_b[, k]
    }

    phi_boot[, , b] <- phi_b
    scores_boot[, , b] <- fpca_b$xiEst[, 1:n_eig, drop = FALSE]
  }
  
  # Compute CIs for eigenfunctions
  phi_lower <- apply(phi_boot, c(1, 2), quantile, probs = prob[1], na.rm = TRUE)
  phi_upper <- apply(phi_boot, c(1, 2), quantile, probs = prob[2], na.rm = TRUE)
  phi_mean  <- apply(phi_boot, c(1, 2), mean, na.rm = TRUE)
  
  # Compute CIs for scores (across bootstraps)
  score_lower <- apply(scores_boot, c(1, 2), quantile, probs = 0.025, na.rm = TRUE)
  score_upper <- apply(scores_boot, c(1, 2), quantile, probs = 0.975, na.rm = TRUE)
  score_mean  <- apply(scores_boot, c(1, 2), mean, na.rm = TRUE)
  
  # Return results
  list(
    t = t_grid,
    phi_hat = phi_hat,
    phi_mean = phi_mean,
    phi_lower = phi_lower,
    phi_upper = phi_upper,
    scores_hat = scores_hat,
    score_mean = score_mean,
    score_lower = score_lower,
    score_upper = score_upper
  )
}
```

#Positive Affect general
```{r}
ddip <- read.csv("C:/Users/surya/Box/UC_Davis/DDIP_Daily_Final_All.csv")
dyad_ids <- unique(ddip$id_dyad)

# randomly choose 1 or 2 with prob = 0.5
set.seed(123)
suffix <- sample(c("1", "2"), size = length(dyad_ids), replace = TRUE)
dyad_ids_with_suffix <- as.numeric(paste0(dyad_ids, suffix))

ddip_sub <- ddip %>%
  dplyr::filter(id_indiv %in% dyad_ids_with_suffix & day > 0) %>% 
  dplyr::select(id_indiv, day, pa_gral, na_gral, pa_rel, na_rel) %>%
  mutate(
    max_day = max(day),
    min_day = min(day),
    time = (day-min_day)/(max_day-min_day),
    id = id_indiv
  ) %>%
  dplyr::select(id, time, pa_gral)  %>%
  group_by(id) %>%
  mutate(
    mean_pa = mean(pa_gral, na.rm = TRUE),
    c_pa = (pa_gral - mean_pa)
  ) %>% 
  ungroup() %>%
  dplyr::select(id, time, c_pa)

ddip_wide <- ddip_sub %>%
  arrange(id, time) %>%   
  pivot_wider(
    names_from = time,
    values_from = c_pa,
    names_prefix = "t"
  ) %>% as.matrix()

head(ddip_sub)
head(ddip_wide)
```

```{r}
Lt <- ddip_sub %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(t = list(time), .groups = "drop") %>%
  dplyr::pull(t)

Ly <- ddip_sub %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(y = list(c_pa), .groups = "drop") %>%
  dplyr::pull(y)

ddip_fpca <- FPCA(Ly, Lt)
plot(ddip_fpca)
```
```{r}
library(dplyr)
library(ggplot2)

set.seed(456)

n_sample <- 100
sample_ids <- ddip_sub %>%
  distinct(id) %>%
  slice_sample(n = n_sample) %>%
  pull(id)

df_plot <- ddip_sub %>%
  filter(id %in% sample_ids) 

ggplot(df_plot, aes(time, c_pa, group = id, color = factor(id))) +
  geom_line(linewidth = 1) +
  theme_minimal(base_size = 14) +
  labs(
    title = paste("Random Sample of", n_sample, "Subjects with PA (Person-Mean Centered)"),
    x = "Time",
    y = "PA (general)"
  ) +
  theme(legend.position = "none")

```

```{r}
set.seed(123)
boot_results <- bootstrap_fpca_ci(ddip_wide[,-1], nb_boot = 100, 
                                  n_eig = 3, argvals = seq(0, 1, length.out = 95), prob = c(0,1))
```

```{r}
# Plot the first eigenfunction with 95% CI
df_phi1 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 1],
  lower = boot_results$phi_lower[, 1],
  upper = boot_results$phi_upper[, 1]
)

ggplot(df_phi1, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "pink") +
  geom_line(size = 1.2, color = "red") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for First Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```

```{r}
# Plot the second eigenfunction with 95% CI
df_phi2 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 2],
  lower = boot_results$phi_lower[, 2],
  upper = boot_results$phi_upper[, 2]
)

ggplot(df_phi2, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "skyblue") +
  geom_line(size = 1.2, color = "blue") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for Second Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```
```{r}
# Plot the third eigenfunction with 95% CI
df_phi3 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 3],
  lower = boot_results$phi_lower[, 3],
  upper = boot_results$phi_upper[, 3]
)

ggplot(df_phi3, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "lightgreen") +
  geom_line(size = 1.2, color = "darkgreen") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for Third Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```

I will use a linear function or an exponential decay function for the first eigenfunction.

```{r}
#Identifying the exponential decay function using OLS
y <- df_phi1$mean
t <- seq(0,1, length.out = length(y))

dat <- data.frame(t = t, y = y)

fit_exp <- nls(
  y ~ a * exp(-b * t) + c,
  data = dat,
  start = list(
    a = y[1] - tail(y, 1),
    b = 3,
    c = tail(y, 1)
  )
)

dat$y_hat <- predict(fit_exp)

plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_hat, col = "red", lwd = 2)
legend("topright", legend = c("Observed", "Exp fit"),
       col = c("black", "red"), lwd = 2)

summary(fit_exp)
confint(fit_exp)

#Identifying the linear function using OLS
y <- df_phi1$mean
t <- seq(0,1, length.out = length(y))

dat_lin <- data.frame(t = t, y = y)

fit_lin <- lm(
  y ~ t,
  data = dat_lin
)

dat_lin$y_hat <- predict(fit_lin)

plot(t, y, type = "l", lwd = 2)
lines(t, dat_lin$y_hat, col = "red", lwd = 2)
legend("topright", legend = c("Observed", "lin fit"),
       col = c("black", "red"), lwd = 2)

summary(fit_lin)
confint(fit_lin)
anova(fit_exp, fit_lin)

phi1_pred <- function(t){
  coef <- as.numeric(coef(fit_exp))
  return(coef[1] * exp(-1*coef[2] * t) + coef[3])}
```
I will use a quadratic function or a cosine function for the first eigenfunction.

```{r}
# Data
y <- df_phi2$mean
t <- seq(0, 1, length.out = length(y))
dat <- data.frame(t, y)

# Quadratic: y = b0 + b2 t^2
fit_quad <- nls(
  y ~ a*(t)^2 + p,
  data = dat,
  start = list(a = max(abs(y)), p = 0)
)
# Cosine: y = a cos(bt + p)
fit_cos <- nls(
  y ~ a * cos(b * t + p),
  data = dat,
  start = list(a = max(abs(y)), b = 2*pi, p = 0)
)

# Predictions
dat$y_quad <- predict(fit_quad)
dat$y_cos  <- predict(fit_cos)

# Plot
plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_quad, col = "red", lwd = 2)
lines(t, dat$y_cos, col = "blue", lwd = 2)
legend("topright",
       legend = c("Observed", "Quadratic", "Cosine"),
       col = c("black", "red", "blue"),
       lwd = 2)

# Output
summary(fit_quad)
summary(fit_cos)
anova(fit_cos, fit_quad)

phi2_pred <- function(t){
  coef <- as.numeric(coef(fit_cos))
  return(coef[1] * cos(coef[2] * t + coef[3]))}

```
Figuring out which cosine function would fit phi3 best

```{r}
# Data
y <- df_phi3$mean
t <- seq(0, 1, length.out = length(y))
dat <- data.frame(t, y)

# Cosine: y = a cos(bt + p)
fit_cos2 <- nls(
  y ~ a * cos(b * t + p),
  data = dat,
  start = list(a = max(abs(y)), b = pi, p = 0)
)

# Predictions
dat$y_cos  <- predict(fit_cos2)

# Plot
plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_cos, col = "blue", lwd = 2)
legend("topright",
       legend = c("Observed", "Cosine"),
       col = c("black", "blue"),
       lwd = 2)

# Output
summary(fit_cos2)

phi3_pred <- function(t){
  coef <- as.numeric(coef(fit_cos2))
  return(coef[1] * cos(coef[2] * t + coef[3]))}

```
```{r}
newGrid <- seq(0, 1, length.out = 95)
fit_ng <- ConvertSupport(fromGrid = ddip_fpca$workGrid,
                                      toGrid = newGrid,
                                      phi = ddip_fpca$phi)

dat_phi <- as_tibble(cbind(phi1 = fit_ng[,1], phi2 = fit_ng[,2], phi3 = fit_ng[,3],
                           t = round(newGrid, 3)))
```

```{r}
ddip_sub <- ddip %>%
  dplyr::filter(id_indiv %in% dyad_ids_with_suffix & day > 0) %>% 
  dplyr::select(id_indiv, day, pa_gral, na_gral, pa_rel, na_rel) %>%
  mutate(
    max_day = max(day),
    min_day = min(day),
    time = (day-min_day)/(max_day-min_day),
    id = id_indiv
  ) %>%
  dplyr::select(id, time, pa_gral) 

library(lme4)

ddip_final <- ddip_sub %>%
  group_by(id) %>%
  mutate(
    t = round(time, 3)
  ) %>% left_join(dat_phi, by = "t") %>%
  ungroup()


# Fit linear + exp model with random intercepts & slopes
full_model <- lmer(
  pa_gral ~ 
    1 + phi1_pred(t) + phi2_pred(t) + phi3_pred(t) + 
    (1 + phi1_pred(t) + phi2_pred(t) + phi3_pred(t) | id),
  data = ddip_final,
  REML = TRUE
)

full_model_fpca <- lmer(
  pa_gral ~ 
    1 + phi1 + phi2 + phi3 + 
    (1 + phi1 + phi2 + phi3 | id),
  data = ddip_final,
  REML = TRUE
)

summary(full_model)
summary(full_model_fpca)

fit_null <- lmer(
  pa_gral ~ 1 + (1 | id),
  data = ddip_final,
  REML = TRUE
)

#McFadden's pseudo r^2
1 - (logLik(full_model)/logLik(fit_null))
1 - (logLik(full_model_fpca)/logLik(fit_null))

anova(fit_null, full_model_fpca)
```
```{r}
end = Sys.time()
end-begin
```


#Negative Affect
```{r}
# randomly choose 1 or 2 with prob = 0.5
set.seed(222)
suffix <- sample(c("1", "2"), size = length(dyad_ids), replace = TRUE)
dyad_ids_with_suffix <- as.numeric(paste0(dyad_ids, suffix))

ddip_sub <- ddip %>%
  dplyr::filter(id_indiv %in% dyad_ids_with_suffix & day > 0) %>% 
  dplyr::select(id_indiv, day, pa_gral, na_gral, pa_rel, na_rel) %>%
  mutate(
    max_day = max(day),
    min_day = min(day),
    time = (day-min_day)/(max_day-min_day),
    id = id_indiv
  ) %>%
  dplyr::select(id, time, na_gral)  %>%
  group_by(id) %>%
  mutate(
    mean_na = mean(na_gral, na.rm = TRUE),
    c_na = (na_gral - mean_na)
  ) %>% 
  ungroup() %>%
  dplyr::select(id, time, c_na)

ddip_wide <- ddip_sub %>%
  arrange(id, time) %>%   
  pivot_wider(
    names_from = time,
    values_from = c_na,
    names_prefix = "t"
  ) %>% as.matrix()

head(ddip_sub)
head(ddip_wide)
```

```{r}
Lt <- ddip_sub %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(t = list(time), .groups = "drop") %>%
  dplyr::pull(t)

Ly <- ddip_sub %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(y = list(c_na), .groups = "drop") %>%
  dplyr::pull(y)

ddip_fpca <- FPCA(Ly, Lt)
plot(ddip_fpca)
```
```{r}
library(dplyr)
library(ggplot2)

set.seed(456)

n_sample <- 100
sample_ids <- ddip_sub %>%
  distinct(id) %>%
  slice_sample(n = n_sample) %>%
  pull(id)

df_plot <- ddip_sub %>%
  filter(id %in% sample_ids) 

ggplot(df_plot, aes(time, c_na, group = id, color = factor(id))) +
  geom_line(linewidth = 1) +
  theme_minimal(base_size = 14) +
  labs(
    title = paste("Random Sample of", n_sample, "Subjects with NA (Person-Mean Centered)"),
    x = "Time",
    y = "NA (general)"
  ) +
  theme(legend.position = "none")

```

```{r}
set.seed(123)
boot_results <- bootstrap_fpca_ci(ddip_wide[,-1], nb_boot = 100, 
                                  n_eig = 3, argvals = seq(0, 1, length.out = 95), prob = c(0, 1))
```

```{r}
# Plot the first eigenfunction with 95% CI
df_phi1 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 1],
  lower = boot_results$phi_lower[, 1],
  upper = boot_results$phi_upper[, 1]
)

ggplot(df_phi1, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "pink") +
  geom_line(size = 1.2, color = "red") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for First Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```

```{r}
# Plot the second eigenfunction with 95% CI
df_phi2 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 2],
  lower = boot_results$phi_lower[, 2],
  upper = boot_results$phi_upper[, 2]
)

ggplot(df_phi2, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "skyblue") +
  geom_line(size = 1.2, color = "blue") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for Second Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```
```{r}
# Plot the third eigenfunction with 95% CI
df_phi3 <- data.frame(
  t = boot_results$t,
  mean = boot_results$phi_mean[, 3],
  lower = boot_results$phi_lower[, 3],
  upper = boot_results$phi_upper[, 3]
)

ggplot(df_phi3, aes(x = t, y = mean)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "lightgreen") +
  geom_line(size = 1.2, color = "darkgreen") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bootstrap 95% CI for Third Eigenfunction",
    x = "Time",
    y = "Eigenfunction Value"
  )

```

I will use a linear function or an exponential decay function for the first eigenfunction.

```{r}
#Identifying the exponential decay function using OLS
y <- df_phi1$mean
t <- seq(0,1, length.out = length(y))

dat <- data.frame(t = t, y = y)

fit_exp <- nls(
  y ~ a * exp(-b * t) + c,
  data = dat,
  start = list(
    a = y[1] - tail(y, 1),
    b = 3,
    c = tail(y, 1)
  )
)

dat$y_hat <- predict(fit_exp)

plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_hat, col = "red", lwd = 2)
legend("topright", legend = c("Observed", "Exp fit"),
       col = c("black", "red"), lwd = 2)

summary(fit_exp)
confint(fit_exp)

#Identifying the linear function using OLS
y <- df_phi1$mean
t <- seq(0,1, length.out = length(y))

dat_lin <- data.frame(t = t, y = y)

fit_lin <- lm(
  y ~ t,
  data = dat_lin
)

dat_lin$y_hat <- predict(fit_lin)

plot(t, y, type = "l", lwd = 2)
lines(t, dat_lin$y_hat, col = "red", lwd = 2)
legend("topright", legend = c("Observed", "lin fit"),
       col = c("black", "red"), lwd = 2)

summary(fit_lin)
confint(fit_lin)
anova(fit_exp, fit_lin)

phi1_pred <- function(t){
  coef <- as.numeric(coef(fit_exp))
  return(coef[1] * exp(-1*coef[2] * t) + coef[3])}
```
I will use a quadratic function or a cosine function for the first eigenfunction.

```{r}
# Data
y <- df_phi2$mean
t <- seq(0, 1, length.out = length(y))
dat <- data.frame(t, y)

# Quadratic: y = b0 + b2 t^2
fit_quad <- nls(
  y ~ a*(t)^2 + p,
  data = dat,
  start = list(a = max(abs(y)), p = 0)
)
# Cosine: y = a cos(bt + p)
fit_cos <- nls(
  y ~ a * cos(b * t + p),
  data = dat,
  start = list(a = max(abs(y)), b = 2*pi, p = 0)
)

# Predictions
dat$y_quad <- predict(fit_quad)
dat$y_cos  <- predict(fit_cos)

# Plot
plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_quad, col = "red", lwd = 2)
lines(t, dat$y_cos, col = "blue", lwd = 2)
legend("topright",
       legend = c("Observed", "Quadratic", "Cosine"),
       col = c("black", "red", "blue"),
       lwd = 2)

# Output
summary(fit_quad)
summary(fit_cos)
anova(fit_cos, fit_quad)

phi2_pred <- function(t){
  coef <- as.numeric(coef(fit_cos))
  return(coef[1] * cos(coef[2] * t + coef[3]))}

```
Figuring out which cosine function would fit phi3 best

```{r}
# Data
y <- df_phi3$mean
t <- seq(0, 1, length.out = length(y))
dat <- data.frame(t, y)

# Cosine: y = a cos(bt + p)
fit_cos2 <- nls(
  y ~ a * cos(b * t + p),
  data = dat,
  start = list(a = max(abs(y)), b = pi, p = 0)
)

# Predictions
dat$y_cos  <- predict(fit_cos2)

# Plot
plot(t, y, type = "l", lwd = 2)
lines(t, dat$y_cos, col = "blue", lwd = 2)
legend("topright",
       legend = c("Observed", "Cosine"),
       col = c("black", "blue"),
       lwd = 2)

# Output
summary(fit_cos2)

phi3_pred <- function(t){
  coef <- as.numeric(coef(fit_cos2))
  return(coef[1] * cos(coef[2] * t + coef[3]))}

```
```{r}
newGrid <- seq(0, 1, length.out = 95)
fit_ng <- ConvertSupport(fromGrid = ddip_fpca$workGrid,
                                      toGrid = newGrid,
                                      phi = ddip_fpca$phi)

dat_phi <- as_tibble(cbind(phi1 = fit_ng[,1], phi2 = fit_ng[,2], phi3 = fit_ng[,3],
                           t = round(newGrid, 3)))
```

```{r}
library(lme4)

ddip_sub <- ddip %>%
  dplyr::filter(id_indiv %in% dyad_ids_with_suffix & day > 0) %>% 
  dplyr::select(id_indiv, day, pa_gral, na_gral, pa_rel, na_rel) %>%
  mutate(
    max_day = max(day),
    min_day = min(day),
    time = (day-min_day)/(max_day-min_day),
    id = id_indiv
  ) %>%
  dplyr::select(id, time, na_gral)

ddip_final <- ddip_sub %>%
  group_by(id) %>%
  mutate(
    t = round(time, 3)
  ) %>% left_join(dat_phi, by = "t") %>%
  ungroup()


# Fit linear + exp model with random intercepts & slopes
full_model <- lmer(
  na_gral ~ 
    1 + phi1_pred(t) + phi2_pred(t) + phi3_pred(t) + 
    (1 + phi1_pred(t) + phi2_pred(t) + phi3_pred(t) | id),
  data = ddip_final,
  REML = TRUE
)

full_model_fpca <- lmer(
  na_gral ~ 
    1 + phi1 + phi2 + phi3 + 
    (1 + phi1 + phi2 + phi3 | id),
  data = ddip_final,
  REML = TRUE
)

summary(full_model)
summary(full_model_fpca)

fit_null <- lmer(
  na_gral ~ 1 + (1 | id),
  data = ddip_final,
  REML = TRUE
)

#McFadden's pseudo r^2
1 - (logLik(full_model)/logLik(fit_null))
1 - (logLik(full_model_fpca)/logLik(fit_null))

anova(fit_null, full_model_fpca)
```
```{r}
ddip_wide <- ddip_final %>%
  dplyr::select(id, t, na_gral) %>%
  pivot_wider(
    names_from = t,
    values_from = na_gral,
    names_prefix = "t_"
  ) %>%
  filter(rowSums(!is.na(across(-id))) >= 2)%>%
  {
    df <- .
    keep_cols <- colSums(!is.na(df[ , -1])) >= 2
    df <- df[ , c(TRUE, keep_cols)]  # TRUE keeps id
    df
  } %>%
  dplyr::select(-id)

dat_phi_1 <- dat_phi[-95,]

loading0 <- rep(1,nrow(dat_phi_1))
loading1 <- dat_phi_1$phi1
loading2 <- dat_phi_1$phi2

dat_lav <- as.data.frame(ddip_wide)
colnames(dat_lav) <- paste0("y", 1:nrow(dat_phi_1))
l0 <- paste0(loading0, "*y", 1:nrow(dat_phi_1), collapse = " + ")
l1 <- paste0(loading1, "*y", 1:nrow(dat_phi_1), collapse = " + ")
l2 <- paste0(loading2, "*y", 1:nrow(dat_phi_1), collapse = " + ")

growth_mod <- paste0("
  eta0 =~ ", l0, "
  eta1 =~ ", l1, "
  eta2 =~ ", l2, "

  # latent variances & covariance
  eta0 ~~ eta0
  eta1 ~~ eta1
  eta2 ~~ eta2
  eta0 ~~ eta1
  eta0 ~~ eta2
  eta1 ~~ eta2

  # constant residual variance across time
  ", paste0(colnames(dat_lav), " ~~ vare*", colnames(dat_lav), collapse = "\n"), "
")

fit <- growth(
  model = growth_mod,
  data  = dat_lav,
  missing = "fiml", 
  em.h1.iter.max = 10000 
)

summary(fit, standardized = TRUE, fit.measures = TRUE)
```

